\textbf{Designing a Virtual Security Management Layer for Cloud Content}

### 2016-02-09 tex/paper.tex
Added some conclusions

\newpage
\section{Implementation}
\subsection{Background}
\subsubsection{The current system} \label{sec:current_system}
Today a system called battlebinary~\cite{BATTLEBINARY} is used for managing and uploading files,
mostly images, to content delivery networks. The current system does not make use out of the
security features that the CDN's are offering, instead it uses a form of security by obscurity. When
a file is uploaded to a CDN it is open for the public, but its filename is composed out of its
original filename concatenated with a part of the MD5 hash of the content of the file, which makes
it an extremely hard process to access the file on the CDN without access to the original file or a
reference to the URI.

@@

\newpage
\subsection{Load Testing}
Wrk was used to load test the back-end. It is a multi-threaded benchmarking tool for HTTP which can
create large loads. The testing was done locally on a virtual server having 6 CPU cores and 48GB of
RAM. The results that will be analysed are latency and throughput of the server as that will give a 
fair judgement of how well the system can perform.

@@

\subsubsection{CDN Connections}
\fix Describe how the CDN connections are encrypted and secure.

@@

\subsubsubsection{Serving private content}
There are three different ways, that this implementation make use of, to make sure that 
the CDNs serve content in a private manner. The first two are signed URLs and signed cookies, and 
the third is a mixture between one of the first two together with a range of IP
addresses.~\cite{AWSPRIVATE} 
These mechanisms are needed, as explained in Section~\ref{sec:current_system}, to ensure that
assets are not leaked if an attacker manages to find out the URL for the asset.

@@

\newpage
\section{Summary}
\subsection{Conclusions}

>>>>

\newpage
\section{Implementation} \label{sec:implementation}
\subsection{Background}
\subsubsection{The current system} \label{sec:current_system}
Today a system called battlebinary~\cite{BATTLEBINARY} is used for managing and uploading files,
mostly images, to content delivery networks. The current system does not make use out of the
security features that the CDN's are offering, instead it uses a form of security by obscurity. When
a file is uploaded to a CDN it is open for the public, but its filename is composed out of its
original filename concatenated with a part of the MD5 hash of the content of the file, which makes
it an extremely hard process to access the file on the CDN without access to the original file or a
reference to the URI.

@@

\newpage
\subsection{Load Testing} \label{sec:load_testing}
Wrk was used to load test the back-end. It is a multi-threaded benchmarking tool for HTTP which can
create large loads. The testing was done locally on a virtual server having 6 CPU cores and 48GB of
RAM. The results that will be analysed are latency and throughput of the server as that will give a 
fair judgement of how well the system can perform.

@@

\subsubsection{CDN Connections} \label{sec:cdn_connections}
\fix Describe how the CDN connections are encrypted and secure.

@@

\subsubsubsection{Serving private content} \label{sec:private_content}
There are three different ways, that this implementation make use of, to make sure that 
the CDNs serve content in a private manner. The first two are signed URLs and signed cookies, and 
the third is a mixture between one of the first two together with a range of IP
addresses.~\cite{AWSPRIVATE} 
These mechanisms are needed, as explained in Section~\ref{sec:current_system}, to ensure that
assets are not leaked if an attacker manages to find out the URL for the asset.

@@

\newpage
\section{Summary}
\subsection{Conclusions}
The goal of this thesis was to see whether it was feasible to use copy-on-write in a high level
application. As the implementation (see Section~\ref{sec:implementation}) made as a part of this 
thesis project is already replacing its predecessor the simple conclusion is that it definitely is 
possible. In the beginning of the project thoughts were on having every element being operated upon
in a copy-on-write fashion but this was later narrowed down to only have the most important part,
the files, as copy-on-write. This was due to that the conclusion that it did not matter if the 
other elements were resolved in a last-write-wins manner when modified.

\par If this application would be distributed with several persistent storage nodes like MongoDB, the
application would not always be in a global consistent state as there would not be any global locks.
This could theoretically cause some inconvenience for the user but in all real world tests no 
users have noticed it. The theoretical inconvenience for the user was a trade-off made so that the
application could scale on the width almost endlessly, especially if the issue with building the
project trees is (as mentioned in Section~\ref{sec:load_testing}) solved.

\par The positive effects of deploying Perius instead of its predecessor was not only on about
scaling, it also features a more secure way of handling private assets 
(Section~\ref{sec:current_system},~\ref{sec:private_content}) and reduces the
administration needed to control the security settings of large groups of assets
(Section~\ref{sec:cdn_connections}) at the same time.
